---
title: "Exploratory Data Analysis Project"
author: Patrick Coakley
date: March 20, 2017
output: html_document
theme: united
---

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, Packages}

install.packages('ggplot2', repos = "http://cran.us.r-project.org")
install.packages('dplyr', repos = "http://cran.us.r-project.org")
install.packages('gridExtra', repos = "http://cran.us.r-project.org")
install.packages('GGally', repos = "http://cran.us.r-project.org")

library(ggplot2)
library(gridExtra)
library(dplyr)
library(GGally)

```

```{r echo=FALSE, Load_the_Data}
# Load the Data
wineData <- read.csv('wineQualityReds.csv')
```

# Background

> Using the sample data set provided by Udacity, we are going to look at the 
different chemical properties of red wine and try to decide if there is a 
relationship between specific variables that make up the wine and their score, 
including sugar, alcohol content, and acidity.

# Variables

```{r echo=FALSE, Head}
names(wineData)
```

> *__Fixed acidity__ - This is what gives wine its bitterness and resistance to 
bacteria, measured by the tartaric acids  
*__Volatile acidity__ - What determines if wine is spoiled or not based on the 
acetic acid levels in the wine  
*__Citric acid__ - Used by some winemakers to increase acidity, though it can 
cause the taste of the wine to be agressively flavored, and is also banned for 
use in the EU and primarily used elsewhere  
*__Residual sugar__ - The natural sugars that reside in the wine after the 
majority are converted to alcohol during the winemaking process  
*__Chlorides__ - The level of sodium chloride in the wine   
*__Free sulfur dioxide__ - The amount of remaining sulfites during and after 
the wine making process  
*__Total sulfur dioxide__ - The total amount of sulfites, including those that 
are not present after the wine making and the free sulfur dioxide  
*__Density__ - The density of the wine   
*__pH levels__ - The pH (potential of hydrogen) levels of the wine used to 
measure the acidty or alkalinity of the wine
*__Sulphates__ - Used during the wine making process to protect the color and 
flavor of the wine, as well as to help prevent the growth of microorganisms  
*__Alcohol__ - The alcohol content of the wine  
*__Quality__ - The rating of the wine  

# Univariate Plots Section

## Summary Of The Data
```{r echo=FALSE, Summary}
summary(wineData)
```
  
## Structure Of The Data
```{r echo=FALSE, Structure}
str(wineData)
```

```{r echo=FALSE, Histograms_List}
library(ggplot2)

wineQualityHist <- qplot(
      data=wineData,
      x=quality,
      xlab='Wine Quality',
      ylab='Count',
      col=I('black'), 
      fill=I('orange'),
      binwidth = .5)

wineAlcoholHist <- qplot(
      data=wineData,
      x=alcohol,
      xlab='Alcohol Content',
      ylab='Count',
      col=I('black'), 
      fill=I('red'))

wineDensityHist <- qplot(
      data=wineData,
      x= density,
      xlab='Density',
      ylab='Count',
      col=I('black'), 
      fill=I('blue'))

wineFreeSulfurHist <- qplot(
      data=wineData,
      x=free.sulfur.dioxide,
      xlab='Free Sulfur Dioxide',
      ylab='Count',
      col=I('black'), 
      fill=I('grey'))

wineTotalSulfurHist <- qplot(
      data=wineData,
      x=total.sulfur.dioxide,
      xlab='Total Sulfur Dioxide',
      ylab='Count',
      col=I('black'), 
      fill=I('grey'))

wineFixedAcidityHist <- qplot(
      data=wineData,
      x= fixed.acidity,
      xlab='Fixed Acidity',
      ylab='Count',
      col=I('black'), 
      fill=I('green'))

wineVolatileAcidityHist <- qplot(
      data=wineData,
      x= volatile.acidity,
      xlab='Volatile Acidity',
      ylab='Count',
      col=I('black'), 
      fill=I('green'))

wineCitricHist <- qplot(
      data=wineData,
      x= citric.acid,
      xlab='Citric Acid',
      ylab='Count',
      col=I('black'), 
      fill=I('green'))

winephHist <- qplot(
      data=wineData,
      x= pH,
      xlab='pH Levels',
      ylab='Count',
      col=I('black'), 
      fill=I('purple'))

wineChloridesHist <- qplot(
      data=wineData,
      x= chlorides,
      xlab='Chlorides',
      ylab='Count',
      col=I('black'), 
      fill=I('purple'))

wineSugarHist <- qplot(
      data=wineData,
      x= residual.sugar,
      xlab='Residual Sugar',
      ylab='Count',
      col=I('black'), 
      fill=I('purple'))

wineSulphatesHist <- qplot(
      data=wineData,
      x= sulphates,
      xlab='Sulphates',
      ylab='Count',
      col=I('black'), 
      fill=I('purple'))
```

## Wine Quality
```{r echo=FALSE, message=FALSE, warning=FALSE, Quality_Histogram}
wineQualityHist + 
               geom_vline(xintercept=mean(wineData$quality), 
                          color="red")
```
  
> Wine quality seems to mostly made up of wines rated at 5 or 6, with very vew 
wines in the extreme. This can be confirmed by looking at the mean and median 
of the quality variable: 

```{r echo=FALSE}
summary(wineData$quality)
```


## Alcohol Content

```{r echo=FALSE}
summary(wineData$alcohol)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, Alcohol_Histogram}
library(gridExtra)
grid.arrange(wineAlcoholHist + 
               geom_vline(xintercept=mean(wineData$alcohol), 
                          color="green"),
             ggplot(aes(x=1, y=alcohol),data = wineData) + 
               geom_boxplot() +
  stat_summary(fun.y = "mean", 
               geom = "point", 
               color = "blue", 
               shape = 3, 
               size = 4), nrow =1)
```

> Based on the summary of the alcohol feature, we can see that the median sits 
at 10.2 and mean at 10.42. Looking at the histogram above, there seems to be a 
large jump at 9% to 9.2%.
  
## Density & pH
```{r echo=FALSE, message=FALSE, warning=FALSE, pH_Histogram}
library(gridExtra)
grid.arrange(winephHist + geom_vline(xintercept=mean(wineData$pH), 
                          color="yellow"),
             wineDensityHist + geom_vline(xintercept=mean(wineData$density), 
                          color="red"))
```

> I put these two together because I found it interesting that their shapes 
were very similar. So similar in fact that I thought I accidentally duplicated 
pH. I think it will be worth investigating their relationship.

## Sulfur Dioxide

```{r echo=FALSE, message=FALSE, warning=FALSE, Sulfur_Dioxide}
grid.arrange(wineFreeSulfurHist 
             + geom_vline(xintercept=mean(wineData$free.sulfur.dioxide), 
                          color="black"),
             wineTotalSulfurHist 
             + geom_vline(xintercept=mean(wineData$total.sulfur.dioxide), 
                          color="black"))
```

## Sulfur Dioxide Log10 Transformation

> As these are long-tailed I decided to do a log10 transformation to see the 
rest of the data better: 

```{r echo=FALSE, message=FALSE, warning=FALSE, Sulfur_Dioxide_Log10}
grid.arrange(wineFreeSulfurHist + scale_x_log10(),
             wineTotalSulfurHist + scale_x_log10())
```

> After the transformation it seems that the free sulfur dioxide is bimodal, 
and there is a large gap at the start of the distribution.  

## Acidity
```{r echo=FALSE, message=FALSE, warning=FALSE, Acidity}
grid.arrange(wineVolatileAcidityHist 
             + geom_vline(xintercept=mean(wineData$volatile.acidity), 
                          color="orange"),
             wineFixedAcidityHist 
             + geom_vline(xintercept=mean(wineData$fixed.acidity), 
                          color="orange"),
             wineCitricHist 
             + geom_vline(xintercept=mean(wineData$citric.acid), 
                          color="orange"))
```

## Suphates, Sugar, & Chlorides
```{r echo=FALSE, message=FALSE, warning=FALSE, Others}
grid.arrange(wineSulphatesHist 
             + geom_vline(xintercept=mean(wineData$sulphates), 
                          color="yellow"),
             wineSugarHist 
             + geom_vline(xintercept=mean(wineData$residual.sugar), 
                          color="yellow"),
             wineChloridesHist 
             + geom_vline(xintercept=mean(wineData$chlorides), 
                          color="yellow"))
```

> As these were all long-tailed and somewhat similar in shape I decided to group 
them together. Interesting to note is that the sugar shape and the chlorides 
shape are somewhat similar, leading me to believe there is a relationship 
between the two.

## Suphates, Sugar, & Chlorides Log10 Transformation
```{r echo=FALSE, message=FALSE, warning=FALSE, Others_Log10}
grid.arrange(wineSulphatesHist + scale_x_log10(),
             wineSugarHist + scale_x_log10(),
             wineChloridesHist + scale_x_log10())
```

> After the transformation, not very much has changed and therefore there are 
no interesting differences between the shapes.

# Univariate Analysis

> There are 1599 types of wine in this data set that have 13 features, including
quality, alcohol content, and density. The quality of the wines is rated from 0 
to 10, with 10 being the best and 0 being the worst. Based on the summary of the 
data, there are no wines rated less than 3, nor are there any higher than 8; 
most wines average a rating of 6. This means that the most popular wines in this
data set were not highly rated.  

> Of the data that jumps out at me, I think the sulfur dioxide features will be 
the most interesting to investigate, as they have quite large ranges, especially 
the free sulfur dioxide, which has a minimum of 1 and a maximum of 72, and an 
average of about 16. This means that there are some outliers that have 
incredibly high amounts of free sulfur dioxide, and I am quite curious to see 
the relationship between those numbers and the rating of the wine. This is also 
the case with the residual sugar as well, where the average is roughly 15% of 
the maximum. Depending on the outcome, it's possible that these stronger 
numbers represent the wines that fall well below or above the average rating.

# Bivariate Plots Section

## Correlation Coefficient Table

```{r echo=FALSE, message=FALSE}
cor(wineData)
```

> I created this just to have it as a reference point when looking for 
possibilities in the data. After creating the table, I decided to first check 
out a few more ideas that looked promising.

## Density, Acidity, and Quality

```{r echo=FALSE}

fixedDensityScatter <- ggplot(data=wineData, 
                              aes(x= fixed.acidity, y= density)) + 
  geom_point(alpha = 1/5, 
  position = position_jitter(h=0), color='purple') +
  geom_smooth(color=I('black'),method = "lm", se = FALSE)


qualVolScatter <- ggplot(data=wineData,  aes(x= quality, 
                                             y= volatile.acidity)) + 
  geom_point(alpha = 1/5, 
  position = position_jitter(h=0), color='purple') +
  geom_smooth(color=I('black'),method = "lm", se = FALSE)
  

qualSulScatter <- ggplot(data=wineData,  aes(x= quality, 
                                             y= sulphates)) + 
  geom_point(alpha = 1/5, 
  position = position_jitter(h=0), color='purple') +
  geom_smooth(color=I('black'),method = "lm", se = FALSE)

grid.arrange(fixedDensityScatter,qualVolScatter,qualSulScatter)

```

> Indeed, after visualizing all three of these in scatter plot form with linear 
trend lines it is easy to see the correlations. In particular, it seems volatile 
acidity is something the negatively effects the wine score, while sulphates 
increases them.

## Alcohol & Quality

> The first thing I decided to take a look at was the relationship between 
alcohol and quality rating. I chose this because ultimately I was curious if 
stronger wines were considered better, or perhaps they're worse because the 
flavor is overpowered.

```{r echo=FALSE, message=FALSE, warning=FALSE, Alcohol_Vs_Quality}
library(dplyr)
qualityGroup <- group_by(wineData, quality)
wineData.alcoholByRating <- summarise(qualityGroup,
                                      alcoholMean = mean(alcohol),
                                      alcoholMedian = median(alcohol),
                                      n = n())
head(wineData.alcoholByRating)

```

> These results are interesting because the vast majority of wines are in the 
80th percentile of alcohol strength, meaning that indeed that the stronger the 
wine the better reviewed it seems to be. This isn't necessarily strong evidence 
since the wines rated 5 make up the biggest group and are actually less than 
the 4 or 3 rated wines, but it is interesting to see that the top rated wines 
also had the biggest mean and median of alcohol. Checking the correlation 
coefficient, we get:

```{r echo=FALSE}
cor(wineData$alcohol,wineData$quality)
```
> This means that there's somewhat of a relationship between the two, but 
nothing too strong.  

```{r echo=FALSE}

ggplot(data=wineData, aes(x= alcohol, 
                           y= quality)) + 
  geom_jitter(alpha=1/2) +
  geom_smooth(color=I('red'),method = "lm", se = FALSE)


```

> We can see that wines rated 5 and above tend to fall into higher levels of 
alcohol. 

## pH & Density
```{r echo=FALSE, ph_Density_Scatter}

ggplot(data=wineData,  aes(x= density, y= pH)) + 
  geom_point(alpha = 1/5, 
  position = position_jitter(h=0), color='blue') +
  geom_smooth(color=I('black'),method = "lm", se = FALSE)

``` 

```{r echo=FALSE}
cor(wineData$pH,wineData$density)
```

> There doesn't seem to be a very strong relationship between pH and density. 
Based on the correlation coefficient, it is simply a weak downhill relationship.

## Sugar & Quality

> I wanted to do a quick comparison similar to the alcohol and quality using 
the residual sugars and quality:

```{r echo=FALSE, Sugar_Vs_Quality}

wineData.sugarByRating <- summarise(qualityGroup,
                                      sugarMean = mean(residual.sugar),
                                      sugarMedian = median(residual.sugar),
                                      n = n())
head(wineData.sugarByRating)

```

> I find it interesting that all of the wines means and medians fall within 0.2 
of each other because, as mentioned previously, the range of residual sugars was
quite large, with a maximum of 15. This means that most wines will be roughly 
the same no matter what rating, so there is no relationship between better 
quality wines and residual sugars, though it does mean that there are still 
some strong outliers that have quite a lot more than most.

```{r echo=FALSE}

ggplot(data=wineData,  aes(x= factor(quality), y= residual.sugar)) + 
  geom_boxplot() +
  stat_summary(fun.y = "mean", 
               geom = "point", 
               color = "blue", 
               shape = 8, 
               size = 1) +
  coord_flip() 

```

## Wider Comparison

> Using the GGally library, we are able to quickly compare all of the variables 
in a matrix plot which can help get a better idea of where the data intersects.

```{r echo=FALSE, message=FALSE, fig.width=14,fig.height=14}
library(GGally)
ggpairs(wineData,
        lower = list(continuous = wrap("points", shape = I('.'))), 
        upper = list(combo = wrap("box", outlier.shape = I('.'))))
```

> I've previously already looked at pH and density, but pH and fixed acidity as 
well as pH and citric acid seem promising.

```{r echo= FALSE}

phCitricScatter <- ggplot(data=wineData,  aes(x= citric.acid, y= pH)) + 
  geom_point(alpha = 1/5, 
  position = position_jitter(h=0), color='blue') +
  geom_smooth(color=I('black'),method = "lm", se = FALSE)


phFixedScatter <- ggplot(data=wineData,  aes(x= fixed.acidity, y= pH)) + 
  geom_point(alpha = 1/5, 
  position = position_jitter(h=0), color='blue') +
  geom_smooth(color=I('black'),method = "lm", se = FALSE)

grid.arrange(phCitricScatter,phFixedScatter)
```

> Sure enough, these look incredibly strong. The correlation coefficient for 
fixed and pH is:

```{r,echo=FALSE, message=FALSE}
cor(wineData$pH,wineData$fixed.acidity)
```

> Next, pH and citric acid are:

```{r,echo=FALSE, message=FALSE}
cor(wineData$pH,wineData$citric.acid)
```

> Both are higher than -0.5, so there is something here. 

```{r echo=FALSE, message=FALSE}

fixedQualityBox<- ggplot(data=wineData, 
       aes(x=factor(quality), y=fixed.acidity)) +
  geom_boxplot() +
  stat_summary(fun.y = "mean", 
               geom = "point", 
               color = "blue", 
               shape = 3, 
               size = 4)

citricQualityBox<- ggplot(data=wineData, 
       aes(x=factor(quality), y=citric.acid)) +
  geom_boxplot() +
  stat_summary(fun.y = "mean", 
               geom = "point", 
               color = "blue", 
               shape = 3, 
               size = 4)

grid.arrange(fixedQualityBox,citricQualityBox)

```

> Using boxplots I decided to put those two features against each level of 
quality, and it's interesting to see that the citric acidity has a linear 
progression in the quality, each rating's median growing higher. It's also 
worth nothing that the the maximum in the lowest rated wines is higher than 
the next highest rating.

## Free Sulfur Dioxide & Quality

```{r echo=FALSE, message=FALSE, warning=FALSE, FreeSulfur_And_Quality}

ggplot(data=wineData, 
       aes(x=factor(quality), y=free.sulfur.dioxide)) +
  geom_boxplot() +
  stat_summary(fun.y = "mean", 
               geom = "point", 
               color = "red", 
               shape = 4, 
               size = 2) +
  ylim(0,45)
```

> There doesn't seem to be much to read into here, but it's interesting to note 
that the 2 most populous ratings, 5 and 6, have the highest medians and maximums 
of free sulfur dioxide.

# Bivariate Analysis

> I was somewhat surprised that alcohol content in the higher rated wines was 
indeed higher than the lower rated ones, as I wasn't sure if there would be any 
kind of relationship between the two. It turned out that alcohol is the 
strongest relation to quality. I was somewhat disappointed residual sugars had 
no impact on the quality, as I was quite sure that the taste and flavor would 
have been strongly related, but in actuality most wines in the data set had the 
same amount of residual sugars, and it doesn't look like it's something that 
defines the wine very much.

> pH and fixed acidity were the strongest bivariate relationship at -0.68, with 
pH and citric acid also fairly strong at -0.54. pH and density were two that I 
thought going into this section would be stronger due to their similar shapes, 
but it did not turn out to be as strong as originally thought. 

> I also noticed that volatile acidity and quality have sit at around -0.39, 
which, while not too huge, is still worth noting. This is also true of 
sulphates, which are the third largest features to effect quality at 0.25. 
Fixed acidity and density are also high at 0.66, which means that the higher 
the fixed acidity the denser the wine is.

# Multivariate Plots Section

> The features that seem to impact quality based on the previous investigations 
are volatile acidity, alcohol, and sulphates. 

## Quality, Volatile Acidity, & Quality

```{r echo=FALSE, Multivariate_Plots}

ggplot(data=wineData, aes(x= quality, 
                           y= sulphates,
                          color= volatile.acidity)) + 
  geom_jitter() +
  geom_smooth(color=I('black'),method = "lm", se = FALSE) +
  scale_colour_gradient2(mid="pink",
                         high="green", 
                         midpoint = 0.8)
  
```

> Volatile acidity does not seem to fall above the middle for most wines, and 
indeed we can see that most of the higher quality wines tend to favor numbers 
closer to 0.4. 

## Sulphates, Alcohol, & Quality

```{r echo=FALSE, Multivariate_Plots2}
  ggplot(aes(x = alcohol, 
             y = sulphates, 
             color = factor(quality)), 
         data = wineData) +
  labs(x='Alcohol[%]',y='Sulphates') +
      geom_point(alpha = 0.75, size = 2) +
      geom_smooth(method = "lm", se = FALSE,size=1)  +
  scale_color_brewer(type='seq',palette = 'Spectral',
                   guide=guide_legend(title='Quality'))
  
```

> This plot is interesting because it shows that higher sulphates are not 
necessarily desired in a higher rated wine, and that most of the highest rated 
wines with stronger alcohol contents also have sulphates that fall between 0.5 
and 1.0.

## Alcohol, Density, & Fixed Acidity

```{r echo=FALSE, Multivariate_Plots3}

ggplot(data=wineData, aes(x= density, 
                           y= fixed.acidity,
                          color= alcohol)) + 
  geom_jitter(alpha=1/2) +
  geom_smooth(color=I('black'),method = "lm", se = FALSE) +
  scale_colour_gradient2(mid="red", 
                         high="green", 
                         midpoint = 9)
  
```

> From this we can take a look at the relationship between density and alcohol, 
and how it is influenced by fixed acidity. Stronger alcohols seem to be less 
dense, and also seem to have lower fixed acidity. Most of the wines with lower 
alcohol levels are denser and have higher fixed acidity numbers.

```{r echo=FALSE}

ggplot(data=wineData, aes(y= pH, 
                           x= density ,
                          color= alcohol)) + 
  geom_jitter(alpha=0.7) +
  scale_colour_gradient2(mid="orange", 
                         high="blue", 
                         midpoint = 9)
```

> I thought this was interesting because it shows that a higher pH is somewhat 
relative to stronger alcohols, and in turn lower density in the wine. This means
that most of the top-rated wines, due to their higher alcohol content, are also 
less dense, and therefore might have higher pH levels than the bulk of the other 
wines.

# Multivariate Analysis

> I think the main takeaway for me was the relationship between density and the 
other aspects of the wine. Higher alcohol content means less dense wine, and 
therefore more than likely higher pH levels and lower fixed acidity levels. 
From this you can surmise that the better wines would have a stronger alcohol 
content, higher pH level, lower fixed acidity levels, and lower density. From 
this discovery I looked into alcohol density, and it turns out that water is 
indeed heavier than alcohol, so that means that less favorable wines might have 
higher water content, or at the very least, less alcohol content and more of 
something else that increases its density.

------

# Final Plots and Summary

### Plot One
```{r echo=FALSE, Plot_One}

  ggplot(aes(x = alcohol, 
             y = sulphates, 
             color = factor(quality)), 
         data = wineData) +
  labs(x='Alcohol[%]',y='Sulphates g / dm3') +
      geom_point(alpha = 0.75, size = 2) +
  scale_color_brewer(type='seq',palette = 'Spectral',
                   guide=guide_legend(title='Quality'))

  
```

### Description One

> I chose this scatter plot because I think it easily shows that lower sulphates 
and higher alcohol levels were favored by higher reviewed wines, which makes 
them both important features when determining what a potentially good wine might 
be made up of.

### Plot Two
```{r echo=FALSE, Plot_Two}
ggplot(data=wineData, aes(x= density, 
                           y= fixed.acidity,
                          color= alcohol)) + 
  geom_jitter(alpha=1/2) +
  geom_smooth(color=I('black'),method = "lm", se = FALSE) +
  scale_colour_gradient2(mid="red", 
                         high="green", 
                         midpoint = 9) +
  labs(title='Alcohol By Fixed Acidity & Density',
       x='Density g / cm^3',
       y='Fixed Acidity g / dm^3',
       color='Alcohol[%]')
  
```

### Description Two

> I chose this for my second plot because it clearly shows in one visualization 
that stronger alcohol levels tend to result in a less dense wine, and in turn 
lower fixed acidity. 

### Plot Three
```{r echo=FALSE, Plot_Three}
qualVolScatter2 <- ggplot(data=wineData,  aes(x= quality, 
                                             y= volatile.acidity)) + 
  geom_point(alpha = 1/5, 
  position = position_jitter(h=0), color='purple') +
  geom_smooth(color=I('black'),method = "lm", se = FALSE) +
  labs(title = 'Quality & Volatile Acidity', 
       x='Quality Rating', y='Volatile Acidity g / dm^3')
  

qualSulScatter2 <- ggplot(data=wineData,  aes(x= quality, 
                                             y= sulphates)) + 
  geom_point(alpha = 1/5, 
  position = position_jitter(h=0), color='purple') +
  geom_smooth(color=I('black'),method = "lm", se = FALSE) +
  labs(title = 'Quality & Sulphates', 
       x='Quality Rating', y='Sulphates g / dm3')


grid.arrange(qualVolScatter2,qualSulScatter2)

```

### Description Three

> Finally, I chose this visualization because it shows that a higher rated wine 
tends to favor higher sulphates and lower volatile acidity, adding to the list 
of features that help us determine a good wine.

------

# Reflection

> I think when doing any sort of exploratory data analysis, it's important to 
have an idea of what you're working with in terms of data sets. I don't have a 
great deal of knowledge with regards to red wine or the science behind wine 
making, so I had to do some preliminary research in order to understand what I 
might want to look for. I think a person's approach to EDA is entirely relative 
to their experience with the data. For example, an expert on wine would already 
understand sulphates and acidity, so they would probably know what kind of 
features to look from the start, where as someone in my position requires a lot 
of time to poke around and try many different ideas before getting to a similar 
conclusion.

> I think  density was the most useful feature of the data set to look at 
because of how it was related to the other parts of the wine that led me to 
figure out what makes a wine reviewed more favorably, meaning better wines 
generally have a stronger alcohol content, higher pH level, lower fixed acidity 
levels, and lower density. This also means that higher density wines are 
generally lower alcohol content, lower pH levels, higher fixed acidity levels, 
and therefore a higher density. 

> For further studies in this data set, I think it would be important to have a 
much better grasp of all the variables involved. For example, had I known the 
science of density and acidity better I might have gotten the same results 
faster, or perhaps even thought of other ways to find some new information. If 
> I were to study this data set more in the future, I think it would be useful 
to have a wider range of data available, especially with regards to the quality.
In this current set, we only have a range of 3 to 8, and I would be curious to 
analyse the very worst (3 or lower) and the very best separately (8 or higher) 
on their own in order to have an isolated look at what makes up their 
compositions separately. I also think that because there are so few higher-rated
wines, the data is not going to be as accurate as it would be for the 
middle-of-the-pack wines, which make up the bulk of the data.

# Sources

University of California Davis  
Waterhouse Lab  
http://waterhouse.ucdavis.edu/whats-in-wine  

Acids In Wines  
Wikipedia  
https://en.wikipedia.org/wiki/Acids_in_wine  

Potassium metabisulfite  
Wikipedia  
https://en.wikipedia.org/wiki/Potassium_metabisulfite#Wine  

Wine Jargon: What is Residual Sugar?  
Serious Eats  
http://drinks.seriouseats.com/2013/04/
wine-jargon-what-is-residual-sugar-riesling-fermentation-steven-grubbs.html  

More Than Organic   
Adding sulphur to wine  
http://www.morethanorganic.com/sulphur-in-wine  

Practical Winery
Issue January/February 2009
https://www.practicalwinery.com/janfeb09/page2.htm  